Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-28 paper.Rnw
knit paper after updating label for hare paper from hare:2016 to hare:2017

In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners. Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}). Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures). See the supporting information for \kge{definitions of the features \sout{additional information on the data}}. The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2016}}.

@@

@
\caption{Example bullet signatures. The bullet signatures correspond to the same land and therefore have very similar patterns. The \citet{hare:2016} random forest is fit using various features that measure the similarity between two such signatures.}
\label{fig:figure-09}
\end{figure}

@@

@
\caption{Parallel coordinate plots of the \citet{hare:2016} random forest predictions from the training (top facet) and testing (bottom facet) data. The observations are separated by known matching (right column) and non-matching (left column) signatures. The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance). Each line corresponds to an observation, and the line color represents the associated random forest probability. There are clear relationships between the feature values and the random forest probabilities.}
\label{fig:figure-10}
\end{figure*}

@@

\kge{We train a new random forest model using \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2016} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons. \kge{See the supporting information for further descriptions of the data.}

>>>>

In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners. Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}). Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures). See the supporting information for \kge{definitions of the features \sout{additional information on the data}}. The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2017}}.

@@

@
\caption{Example bullet signatures. The bullet signatures correspond to the same land and therefore have very similar patterns. The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
\label{fig:figure-09}
\end{figure}

@@

@
\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data. The observations are separated by known matching (right column) and non-matching (left column) signatures. The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance). Each line corresponds to an observation, and the line color represents the associated random forest probability. There are clear relationships between the feature values and the random forest probabilities.}
\label{fig:figure-10}
\end{figure*}

@@

\kge{We train a new random forest model using \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2017} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons. \kge{See the supporting information for further descriptions of the data.}

### 2020-09-28 paper.tex
knit paper after updating label for hare paper from hare:2016 to hare:2017

\end{knitrout}
\caption{Example bullet signatures. The bullet signatures correspond to the same land and therefore have very similar patterns. The \citet{hare:2016} random forest is fit using various features that measure the similarity between two such signatures.}
\label{fig:figure-09}
\end{figure}

@@

\end{knitrout}
\caption{Parallel coordinate plots of the \citet{hare:2016} random forest predictions from the training (top facet) and testing (bottom facet) data. The observations are separated by known matching (right column) and non-matching (left column) signatures. The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance). Each line corresponds to an observation, and the line color represents the associated random forest probability. There are clear relationships between the feature values and the random forest probabilities.}
\label{fig:figure-10}
\end{figure*}

@@

\kge{We train a new random forest model using 83,028 land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2016} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with 364 rows of land comparisons. \kge{See the supporting information for further descriptions of the data.}

>>>>

\end{knitrout}
\caption{Example bullet signatures. The bullet signatures correspond to the same land and therefore have very similar patterns. The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
\label{fig:figure-09}
\end{figure}

@@

\end{knitrout}
\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data. The observations are separated by known matching (right column) and non-matching (left column) signatures. The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance). Each line corresponds to an observation, and the line color represents the associated random forest probability. There are clear relationships between the feature values and the random forest probabilities.}
\label{fig:figure-10}
\end{figure*}

@@

\kge{We train a new random forest model using 83,028 land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2017} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with 364 rows of land comparisons. \kge{See the supporting information for further descriptions of the data.}
